Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-20 manuscript.tex
Update manuscript.tex
push REV1
Update on Overleaf.

% !TeX TS-program = pdfLaTeX
% !TeX encoding = UTF-8 Unicode
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
% https://www.overleaf.com/project/633bf90497b5b325a3ff692e
% https://framateam.org/spikeai/channels/review_polychrony
% https://www.zotero.org/groups/4562620/polychronies
%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ResponseReviewerTwo}{
We would like to thank reviewer 2 for his very detailed response which were essential in providing this new revision.

@@

% role of myelination and neuronal delay

\citet{fields_new_2015, fields_myelin_2020} state that myelin facilitates both the neural circuit function and the behavioral performance: experiments on mammals show that myelinization is activity-dependent and directly related to learning and memory consolidation, especially sensory or motor training and in enriched environments. This biological phenomenon takes place both at an early age, where the amount of oligodendrocites is particularly high in the central nervous system~\citep{reynolds_study_1928}, and in older animals, due to its involvement in coupling the activity of distant neuron populations. Myelination helps memory consolidation by coupling the activity of distant neuron populations and generating nearly synchronous responses in postsynaptic neurons involved among others in path integration~\citep{madadi_asl_dendritic_2018}, as was experimentally demonstrated on mice using a Morris water maze~\citep{steadman_disruption_2020}, contextual fear conditioning~\citep{pan_preservation_2020} or oligodendrocyte precursor cells (OPCs) knock-out~\citep{wan_impaired_2020}. Myelin also inhibits axon sprouting and synapse formation, especially in pyramidal neurons~\citep{fields_new_2015}, and is involved in axonal energy saving through a reduced axonal capacitance and a shift of the metabolic load from axons onto oligodendrocytes~\citep{duncan_neuron-oligodendrocyte_2021}.

@@

\dataavailability{This works is made reproducible using the following tools. First the manuscript's source code, and the code reproducing all figures is available on \href{https://github.com/SpikeAI/XXX}{GitHub}. %~\citep{Grimaldi2023review}. 
The paper is available as an \href{https://arxiv.org/abs/YYYY.XXX}{arXiv preprint} with links to previous versions. Find the associated \href{https://www.zotero.org/groups/4562620/polychronies}{Zotero group} which was used to regroup relevant literature on the subject.}

\acknowledgments{We would like to thank Hugo Ladret and Frdéric Chavane for valuable feedback while writing this review. Many thanks to Simon Thorpe for the useful discussions and references on the latency of the visual system in human and non-human primates.}

>>>>

% !TeX TS-program = pdfLaTeX
% !TeX encoding = UTF-8 Unicode
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% REV1
%
% https://www.overleaf.com/project/633bf90497b5b325a3ff692e
% https://framateam.org/spikeai/channels/review_polychrony
% https://www.zotero.org/groups/4562620/polychronies
%%%%%%%%%%%%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ResponseReviewerTwo}{
We would like to thank reviewer 2 for his very detailed response which were essential in providing this new revision.

@@

% role of myelination and neuronal delay
\citet{fields_new_2015, fields_myelin_2020} state that myelin facilitates both the neural circuit function and the behavioral performance: experiments on mammals show that myelinization is activity-dependent and directly related to learning and memory consolidation, especially sensory or motor training and in enriched environments. This biological phenomenon takes place both at an early age, where the amount of oligodendrocites is particularly high in the central nervous system~\citep{reynolds_study_1928}, and in older animals, due to its involvement in coupling the activity of distant neuron populations. Myelination helps memory consolidation by coupling the activity of distant neuron populations and generating nearly synchronous responses in postsynaptic neurons involved among others in path integration~\citep{madadi_asl_dendritic_2018}, as was experimentally demonstrated on mice using a Morris water maze~\citep{steadman_disruption_2020}, contextual fear conditioning~\citep{pan_preservation_2020} or oligodendrocyte precursor cells (OPCs) knock-out~\citep{wan_impaired_2020}. Myelin also inhibits axon sprouting and synapse formation, especially in pyramidal neurons~\citep{fields_new_2015}, and is involved in axonal energy saving through a reduced axonal capacitance and a shift of the metabolic load from axons onto oligodendrocytes~\citep{duncan_neuron-oligodendrocyte_2021}.

@@

\dataavailability{This work is made reproducible using the following tools. First the manuscript's source code, and the code reproducing all figures are available on \href{https://github.com/SpikeAI/XXX}{GitHub}. %~\citep{Grimaldi2023review}. 
The paper is available as an \href{https://arxiv.org/abs/YYYY.XXX}{arXiv preprint} with links to previous versions. Find the associated \href{https://www.zotero.org/groups/4562620/polychronies}{Zotero group} which was used to regroup relevant literature on the subject.}

\acknowledgments{We would like to thank Hugo Ladret and Frédéric Chavane for valuable feedback while writing this review. Many thanks to Simon Thorpe for the useful discussions and references on the latency of the visual system in human and non-human primates.}
